---
title: "README"
author: "Gabe Lord"
date: "May 31, 2019"
output: html_document
---


This app is intended to take information from the city of Chicago concerning
restaurants and their health inspection violations

The goal of this app is to allow the user to see what restaurants are at what 
risk levels and whether they passed their inspection

Below is the list of packages used in the creation and use of this app


```{r setup, include=FALSE}
library(tidyverse)
library(plyr)
library(dplyr)


library(RPostgreSQL) 
library(postGIStools)
library(rgdal)
library(rgeos)
library(sp)
library(tmap)
library(leaflet)
library(raster)
library(sf)
library(RQGIS)
library(shiny)
```


Information was taken from the city of Chicago data portal

the csv was changed into a shapefile using QGIS

```{r}
chi_rest <- readOGR(".", "chicago_restaurant")
```

```{r}
chi_rest2 <- st_as_sf(chi_rest)
```

```{r}
chi_rest2 <- subset(chi_rest2, select = -c(AKA.Name, License.., Facility.T, 
                                         City, State, Zip, 
                                         Inspection, Inspecti_1))
```

```{r}
chi_rest3 <- head(chi_rest2, 100)
```


```{r}
crs(chi_rest)
```

```{r}
chi_rest3 = st_transform(chi_rest3, 4326)
```



Below is the most recent attempt to fix the app. Errors are detailed below this 
block of code

```{r}

# Define UI for application that filters map points based on year and minimum population
ui <- fluidPage(
   
   # Application title
   titlePanel("Restaurants in Chicago"),
   
   # Sidebar with a slider input for year, numeric input for population 
   sidebarLayout(
      sidebarPanel(

          selectInput("risk", label = h3("Risk"), 
                      choices = list("Risk 1 (High)" = 1,
                                     "Risk 2 (Medium)" = 2,
                                     "Risk 3 (Low)" = 3), 
                      selected = 1),
  
         
         radioButtons("results", label = h3("Results"), 
                      choices = list("Passed" = 1,
                                     "Passed w/ Conditions" = 2,
                                     "Fail" = 3), 
                      selected = 1)
      ),
      
      # Show the map and table
      mainPanel(
         leafletOutput("chi_rest3")
      )
   )
)

# Define server logic required to draw a map and table
server <- function(input, output) {

   
   output$chi_rest3 <- renderLeaflet({
    chi_rest3 <- filter(risk == input$Risk,
                        result == input$Result)
     leaflet(data = chi_rest3) %>%
       addTiles() %>%
       addMarkers()
   })
}

# Run the application 
shinyApp(ui = ui, server = server)
```

I tried to plot the entire data set but it is too large and would crash r every 
time. 
After cutting the data down, the shapefile plotted but it was in the wwrong 
location
I have tried changing the CRS (which is currently set to (
+proj=utm +zone=16 +datum=WGS84 +units=m +no_defs).
after trying to run
I tried st_set_crs() andmake_EPSG() but neither worked
After this I tried st_transform(x, 4326) which finally worked for plotting.

Unfortunately I am still trying to get me widgets to work with my data
